Model

### 2019-04-17 stats/model.Rmd
infer sem knowledge model update

    var conditionData = _.filter(data, {condition: cndtn})

    var sem_slope = uniformDrift({a: -5, b: 5, width: 0.2})
    var sem_int = uniformDrift({a: 0, b: 5, width: 0.2})

@@

@@

    return extend([
      {int: sem_int, slope: sem_slope, familiar: cndtn}
    ])

@@

sem_know_model<- webppl(
  program_code = paste(rsaUtils, rsaModel, semStr , sep='\n'),
  data = list(data = me_model_data),
  data_var = "dataFromR",
  model_var = "model",
  chains = 4,
  cores = 4,
  inference_opts = list(method = "MCMC", samples = 5000, burn = 2000, verbose = T)
)

sem_know <- sem_know_model %>%
  select(value) %>%
  map_df(bind_rows)%>%
  rename(int = `0.int`,
         slope = `0.slope`,
         familiar = `0.familiar`)%>% 
  gather(parameter, value, -familiar)

@@

plot_sem_know <- sem_know_params%>%
  select(-uci,-lci)%>%
  spread(parameter, -familiar)%>%
  expand(familiar, slope, int,age = me_model_data$age)%>%
  mutate(sem_know = plogis(int + slope * age))%>%
  left_join(aoa_ratings)%>%
  ungroup()%>%
  mutate(familiar = fct_reorder(factor(familiar), mean_aoa))

>>>>

    var conditionData = _.filter(data, {familiar: cndtn})

    var sem_slope = uniformDrift({a: -2, b: 2, width: 0.2})
    var sem_int = uniformDrift({a: 0, b: 5, width: 0.2})

    // var so_slope = uniformDrift({a: -2, b: 2, width: 0.2})
    // var so_int = uniformDrift({a: -2, b: 2, width: 0.2})

@@

      // var speakerOptimality = so_int  + so_slope * age

@@

    return extend([
      {sem_int: sem_int, sem_slope: sem_slope, familiar: cndtn}
    ])

@@

sem_know_model<- webppl(
  program_code = paste(rsaUtils, rsaModel, semStr , sep='\n'),
  data = list(data = me_model_data),
  data_var = "dataFromR",
  model_var = "model",
  chains = 4,
  cores = 4,
  inference_opts = list(method = "MCMC", samples = 1000, burn = 1000, verbose = T)
)

sem_know <- sem_know_model %>%
  select(value) %>%
  map_df(bind_rows)%>%
  rename(sem_int = `0.sem_int`,
         sem_slope = `0.sem_slope`,
         familiar = `0.familiar`)%>%
         #so_int = `0.so_int`,
         #so_slope = `0.so_slope`)%>% 
  gather(parameter, value, -familiar)

@@

plot_sem_know <- sem_know_params%>%
  select(-uci,-lci)%>%
  spread(parameter, -familiar)%>%
  expand(familiar, sem_slope, sem_int,age = me_model_data$age)%>%
  mutate(sem_know = plogis(sem_int + sem_slope * age))%>%
  left_join(aoa_ratings)%>%
  ungroup()%>%
  mutate(familiar = fct_reorder(factor(familiar), mean_aoa))
